Technical Report

### 2017-10-03 fully-abstract-comp/technical-report.tex
typo
Added a short section on related work and a bibtex file

@@

\begin{definition}
  \label{def:program}
  \lau{27-09-2017: The ``somehow''s need to be fixed.}
  A program consists of two sealed capabilities, $\vsc_\code = \sealed{c_\code,\sigma}$ and $\vsc_\data = \sealed{c_\data,\sigma}$, and and two memory segments $\ms$ and $\ms_\link$ satisfying
  \begin{itemize}
  \item $c_\code = ((\rx,\lin_\code),\baddr_\code,\eaddr_\code,\aaddr_\code)$ where $\aaddr = \baddr + 3$ and $[\baddr_\code,\eaddr_\code]\subseteq \dom(\ms)$
  \item $c_\data = ((\rw,\lin_\data),\baddr_\data,\eaddr_\data,\baddr_\data)$ where $[\baddr_\data,\eaddr_\data] \subseteq \dom(\ms)$ and $[\baddr_\code,\eaddr_\code] \cap [\baddr_\data,\eaddr_\data] = \emptyset$
  \item $\ms$ and $[c_\code,c_\data]$ are self-contained with $\ms_\link$ as slack.
  \item $\ms(\baddr_\code) = \seal(\normal,\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr)$ where these are somehow the sufficient amount of seals.
  \item $\ms(\baddr_\code+1) = ((\ro,\normal),\baddr_\link, \eaddr_\link, \baddr_\link)$ where $\dom(\ms_\link) = [\baddr_\link, \eaddr_\link]$
  \item $\ms(\baddr_\code+2) = \dots$ where $\dots$ is somehow the stack height.
  \end{itemize}
\end{definition}
\lau{27-09-2017: At the moment, we do not have the proper support to let the code capability be linear (in the sense that you cannot write a sensible program) - maybe we should just require the code capability to be normal.}

@@

\end{document}

>>>>

% References
\usepackage{natbib}
\bibliographystyle{plainnat}

@@

\begin{definition}
  \label{def:program}
  \lau{27-09-2017: The ``somehow''s need to be fixed.}
  A program consists of two sealed capabilities, $\vsc_\code = \sealed{c_\code,\sigma}$ and $\vsc_\data = \sealed{c_\data,\sigma}$, and and two memory segments $\ms$ and $\ms_\link$ satisfying
  \begin{itemize}
  \item $c_\code = ((\rx,\lin_\code),\baddr_\code,\eaddr_\code,\aaddr_\code)$ where $\aaddr = \baddr + 3$ and $[\baddr_\code,\eaddr_\code]\subseteq \dom(\ms)$
  \item $c_\data = ((\rw,\lin_\data),\baddr_\data,\eaddr_\data,\baddr_\data)$ where $[\baddr_\data,\eaddr_\data] \subseteq \dom(\ms)$ and $[\baddr_\code,\eaddr_\code] \cap [\baddr_\data,\eaddr_\data] = \emptyset$
  \item $\ms$ and $[c_\code,c_\data]$ are self-contained with $\ms_\link$ as slack.
  \item $\ms(\baddr_\code) = \seal{\normal,\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr}$ where these are somehow the sufficient amount of seals.
  \item $\ms(\baddr_\code+1) = ((\ro,\normal),\baddr_\link, \eaddr_\link, \baddr_\link)$ where $\dom(\ms_\link) = [\baddr_\link, \eaddr_\link]$
  \item $\ms(\baddr_\code+2) = \dots$ where $\dots$ is somehow the stack height.
  \end{itemize}
\end{definition}
\lau{27-09-2017: At the moment, we do not have the proper support to let the code capability be linear (in the sense that you cannot write a sensible program) - maybe we should just require the code capability to be normal.}

@@

\section{Related Work}
\subsection{Conditional Full-Abstraction}
The idea of conditional full-abstraction was used by \citet{Juglaret2016} to define full abstraction for unsafe languages. Their definition requires both the programs and the context to be fully defined (i.e.\ not cause undefined behavior). If the programs are not required to be fully-defined, then anything can happen which makes it impossible to reason about.. In our work, undefined behavior marks cases that we do not want to consider because they should be excluded further up in the compilation chain. Further, if we have to take these cases into account, then we need to add checks which protects the trusted code against itself, but properly compiled code should not have to protect itself against itself.
\lau{03-10-2017: We can adjust this when we have actually done something.}

\bibliography{references}
\end{document}
